Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/impl.tex
changes suggested by Frank

To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls. 
The results suggest that the overhead of tracking correlated calls is very minor: the running times of the two analyses are roughly the same, ranging from 
a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each case (see the Appendix
for detailed results).
%This suggests that the overhead of tracking correlated calls is manageable,
%and that our technique may be worthwhile in other scenarios.  
For the specific combination of this IFDS client analysis and these benchmark
programs, tracking correlated calls did not impact precision.

>>>>

To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls. 
The results suggest that the overhead of tracking correlated calls is minor: the running times of the two analyses are roughly the same,
except on the \texttt{javac} benchmark, where the correlated-calls analysis takes about twice as long as the equivalence analysis.
The absolute times range from 
a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} (see the Appendix
for detailed results).
Our implementation is a research prototype and many opportunities for
optimization remain.
%This suggests that the overhead of tracking correlated calls is manageable,
%and that our technique may be worthwhile in other scenarios.  
For the specific combination of this IFDS client analysis and these benchmark
programs, tracking correlated calls did not impact precision.
